\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome5}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

% \begin{center}
%     {\Huge \textbf{Devanshi Jain}} \\
%     \vspace{1pt}
    
%     % San Diego,California \\ \vspace{1pt}
%     \small \href{tel:+1(858)214-4291}{\raisebox{-0.1\height}\faPhone\ {(858)214-4291} ~} 
%     \href{mailto:djain@ucsd.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{djain@ucsd.edu} ~} 
%     \href{https://linkedin.com/in/djain18}{\raisebox{-0.2\height}{\faLinkedin}\ \underline{djain18} ~}
%     \href{https://github.com/devanshi-jain}{\raisebox{-0.2\height}\faGithub\ \underline{devanshi-jain} ~}
%     % \small {San Diego, California}
%     {\raisebox{-0.2\height}\faMapMarker\  {San Diego, CA}} ~ 
%     % \href{https://linkedin.com/in/djain18}
%     \vspace{-8pt}
% \end{center}

{\Huge \textbf{Devanshi Jain}} \\
\vspace{1pt}

\begin{center}
    \small 
    \href{tel:+1(858)214-4291}{\faPhone\ {(858)214-4291} ~} 
    \href{mailto:djain@ucsd.edu}{\faEnvelope\  \underline{djain@ucsd.edu} ~} 
    \href{https://linkedin.com/in/djain18}{\faLinkedin\ \underline{djain18} ~}
    \href{https://github.com/devanshi-jain}{\faGithub\ \underline{devanshi-jain} ~}
    {\faMapMarker\  {San Diego, CA}} ~ 
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego - \textit{\textbf{Junior}}}{2021 -- 2024}
      {Bachelor of Science - \textbf{Mathematics \& Computer Science}}{GPA: 3.4}
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{EXPERIENCE}
\vspace{5pt}
\resumeSubHeadingListStart
  \resumeSubheading
    {Software Engineering Intern : Distributed Energy Resources Connect}{Oct 2022 -- Present}
    {\underline{}}{\vspace{-15pt}}
    \resumeItemListStart
      \resumeItem{Developed and implemented efficient algorithms for plug load controller scheduling, resulting in
      \textbf{improved energy optimization} and reduced operational costs.}
      \resumeItem{\textbf{Collaborated with a cross-functional team} to integrate optimization algorithms into the existing testbenches, ensuring seamless functionality and compatibility.}
      \resumeItem{\textbf{Conducted comprehensive data analysis} of energy consumption patterns using InfluxDB and presented key insights to stakeholders, enabling data-driven decision-making.}
      \resumeItem{\textbf{Contributed to the design and implementation} of a user-friendly interface for the plug load controller scheduler, enhancing usability and accessibility for end-users.}
      \resumeItem{\textbf{Participated in regular code reviews and quality assurance activities}, ensuring code quality, identifying bugs, and implementing necessary fixes for optimal performance.}
      \resumeItem{\textbf{Collaborated with the data visualization team} to create informative and visually appealing heatmaps, aiding in the identification of energy consumption trends and patterns.}
      \resumeItem{\textbf{Demonstrated strong problem-solving skills} by resolving technical issues and optimizing the performance of the plug load controllers, contributing to a more reliable and efficient system.}
    \resumeItemListEnd
  \vspace{-7pt}

  \resumeSubheading
    {Embedded Systems Engineer : Triton Robosub}{Nov 2021 -- Present}
    {\underline{}}{\vspace{-15pt}}
    \resumeItemListStart
      \resumeItem{\textbf{Passion for marine robotics} and a strong background in the development and deployment of \underline{autonomous underwater vehicles}.}
      \resumeItem{Scripted signal processing algorithms including extraction algorithms such as for \underline{peak detection using cumulative probability}, resulting in improved accuracy and robustness of signal analysis.}
      \resumeItem{Implemented algorithms for direction finding in a hardware-efficient manner on an FPGA. Utilized Xilinx IP to initiate AXI-Lite transactions in simulation to test and validate the implementation.}
      \resumeItem{Integration of the MUSIC algorithm in Python into the control system of the AUV involved using Vivado to generate RTL for the FPGA by \underline{High-level synthesis} of the C script.}
      \resumeItem{Designed and \underline{optimized the hydrophone array} system to accurately perceive the underwater environment.}
    \resumeItemListEnd

  \resumeSubheading
    {Research Assistant : Bioinspired Robotics and Design Lab}{Aug 2022 -- Sept 2022}
    {\underline{}}{\vspace{-15pt}}
    \resumeItemListStart
      \resumeItem{Worked as part of a team on an aquatic soft robotics project to develop a cephalopod-inspired robot capable of cyclic jet propulsion using directional control valves, microcontrollers, and air compressors for shape change.}
    \resumeItemListEnd

  \resumeSubheading
    {Teaching Assistant : COSMOS Hacking for Oceans}{Jun 2022 -- Jul 2022}
    {\underline{}}{\vspace{-15pt}}
    \resumeItemListStart
      \resumeItem{Assisted course instructor in teaching students ways to build an autoboat with a buoy, how to monitor, generate and analyze collected sensor data, and use data visualization and analysis tools to present findings.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{\normalsize{Languages:}}{\normalsize{ SystemVerilog, Python, Java, C, C++, MATLAB, Julia, SageMath, HTML, CSS.}} \\
    \textbf{\normalsize{Developer Tools:}}{\normalsize{ Xilinx Vivado, Visual Studio, Jupyter, OpenGL, Eclipse, LaTeX, Linux, Github, InfluxDB }} \\
  }}
\end{itemize}
\vspace{-15pt}

% %-----------MATH RESEARCH-----------
% \section{RESEARCH \& MATH}
% % Translational Surfaces
% \resumeSubheading
% {Independent Reading Groups}{}
% {\underline{}}{}
% \vspace{-15pt}
% \resumeItemListStart
% \resumeItem{\normalsize{\underline{Operator Algebra:} Studying Banach spaces, Hilbert spaces, and properties of bounded linear operators.}}
% \resumeItem{\normalsize{\underline{Random Matrix Theory:} Studied Wigner Matrices \& Semicircle Law, convergence of moments in expectation.}}
% \resumeItem{\normalsize{\underline{Translational Surfaces:} Studied unfolding of billiard tables, Euler characteristics, stratum, \& Veech surfaces.}}
% \resumeItemListEnd

%-----------CERTIFICATIONS---------------
\section{AWARDS \& FELLOWSHIPS}
\begin{multicols}{2}
\begin{itemize}[itemsep=-2pt, parsep=5pt]
  \item{Led a 3-part Putnam workshop series on number theory, combinatorics, and algebra - 2021}
  \item{Mathematical Contest in Modeling (COMAP) - Analytic Measures' Github - 2022}
  \item{{KVPY Fellow - Indian Institute of Science - 2019,20}}
  \item{Code In Place - Stanford University - 2021}
  \item{National Scholar - IIT Delhi - 2019}
  \item{Regional Mathematics Olympiad - 2017,18,19,20}
  \item{Ramanujan Society of Born Mathematics - 2016,20}
  \item{South-East Asian Mathematics Olympiad - Bronze Medal - 2018}
  \item{International Informatics Olympiad - Silver - 2018}
\end{itemize}
\end{multicols}
\vspace*{2.0\multicolsep}
\end{document}